---
title: "Jennings Invertrbrate Community"
author: "Colleen Cosgrove"
date: "4 October 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r combine datasets}
#Combine the four individual CSVs from each sample date
#Note to self: never do in a new tab what you can do in a new column...

#smartbind in gtools can combine datasets
library(gtools)

##Load invert community files and merge them into one csv file.
date4=read.csv("C:/Users/Colleen/Dropbox/Jennings Invertebrates/beerbottles_10.15.16.csv")
date4[is.na(date4)]<-0
date4=date4[c(1:93),c(1:129)]
date3=read.csv("C:/Users/Colleen/Dropbox/Jennings Invertebrates/beerbottles_8.10.16.csv")
date3[is.na(date3)]<-0
date3=date3[c(1:95),c(1:115)]
date2=read.csv("C:/Users/Colleen/Dropbox/Jennings Invertebrates/beerbottles_5.15.16.csv")
date2[is.na(date2)]<-0
date2=date2[c(1:95),c(1:117)]
date1=read.csv("C:/Users/Colleen/Dropbox/Jennings Invertebrates/beerbottles_10.6.15.csv")
date1[is.na(date1)]<-0
date1=date1[c(1:91),c(1:80)]
colnames(date1)

commdata=smartbind(date1,date2,date3,date4)
write.csv(commdata)

#Once datasets are combined, check to make sure no misspellings in col names
colnames(commdata)

#remove any NAs
is.na(commdata[,1])
#91,186,281,374 = rows with all NA's
commdata=commdata[-c(91,186,281,374),]
commdata[is.na(commdata)]<-0
is.na(commdata)

write.csv(commdata,"invertcommdata2.csv")
```

For the EntSA poster:
1. Totals by ecosystem, data
2. Gamma diversity between ecosystems
3. RDA


```{r Load data}
#SET UP

#Load Data
commdata=read.csv("C:/Users/Colleen/OneDrive/Documents/School/Research/Data/Inverts/invertcomm/invertcommdata.csv", header=T)
treedata=read.csv("C:/Users/Colleen/Dropbox/Jennings 2016/New Adult Basal Area.csv")
soildata=read.csv("C:/Users/Colleen/OneDrive/Documents/School/Grad School/SpatialStats/soil data May 08 for tree plots.csv")
dim(soildata)
treedata[is.na(treedata)] <- 0
treedata=treedata[treedata$ecosys!="S",] #Remove the stream plots -- Will need to put these back in when I fix the commdata$ecosystem columns.
dim(treedata)
##Tree SPP which are OVER 1% of total basal area: ACERUB, ACESAC, CARCOR, CAROVA, FAGAME, FRAAME, LIRTUP, PLAOCC, POPDEL, PRUSER, QUEALB, QUEPAL, QUERUB, TILAME

tree.ringsum=treedata[1:83,]
for(i in 1:83) {
	tree.ringsum3=treedata[i,10:42]+treedata[i+83,10:42]+treedata[i+166,10:42]  }
for(i in 1:83) {
	tree.ringsum2=treedata[i,10:42]+treedata[i+83,10:42] }
for(i in 1:83) {
	tree.ringsum1=treedata[i,10:42] }
rownames(tree.ringsum)=tree.ringsum[,1]

library(vegan)
library(packfor)
library(nlme)
dim(commdata)

#Separate out dates for future lines of code:
date4=commdata[commdata$Date=="10.15.16",]
date2=commdata[commdata$Date=="5.5.16",]
date3=commdata[commdata$Date=="8.10.16",]
date1=commdata[commdata$Date=="10.6.15",]
```

```{r Exploratory Stats}
#General summation and graph by date
sum(commdata$Total) #Total=99517 individuals
plot(commdata$Total~commdata$Date) #Most individuals in falls
dateordered=ordered(commdata$Date, levels = c("10.6.15","5.5.16","8.10.16","10.15.16"))
sumplot=boxplot(commdata$Total~dateordered, xlab="Date", ylab="Average Site Sum")
sumplot2=boxplot(commdata$Total~dateordered, xlab="Date", ylab="Average Site Sum", ylim=c(0,1000))



ecoplot=plot(commdata$Total~commdata$Habitat, xlab="Ecosystem", ylab="Average Ecosystem Sum")
ecoplot2=plot(commdata$Total~commdata$Habitat, xlab="Ecosystem", ylab="Average Ecosystem Sum", ylim=c(0,1000))

#abundance by date and ecosystem
abund=aov(commdata$Total~commdata$Habitat*commdata$Date)
summary(abund)
plot(abund)
shapiro.test(commdata$Total)
#shapiro.test is super non-normal; log transform best transforms the datam but not great..
sqtot=lm(commdata$Total)
abund1=aov(sqtot~commdata$Habitat*commdata$Date)
summary(abund1)
plot(abund1)
shapiro.test(sqtot)
TukeyHSD(abund1)


#sum by date and ecosystem
date4=commdata[commdata$Date=="10.15.16",]
sum(date4$Total)
date2=commdata[commdata$Date=="5.5.16",]
sum(date2$Total)
date3=commdata[commdata$Date=="8.10.16",]
sum(date3$Total)
date1=commdata[commdata$Date=="10.6.15",]
sum(date1$Total)

Bot=commdata[commdata$Habitat=="B",]
sum(Bot$Total)
rip=commdata[commdata$Habitat=="BD"|commdata$Habitat=="DB",]
sum(rip$Total)

```

```{r Diversity}
#Gamma diversity between ecosystems
rownames(date1)=date1[,1]
dim(date1)
Hdate1=diversity(date1[1:89,8:158])
raredate1=rarefy(date1[,8:158], 2)-1
specno=specnumber(commdata[8:158], MARGIN=1)

botrich=lme(specno~asfactor(commdata$TerrType)*commdata$Date+commdata$Plot)
summary(botrich)
TukeyHSD(botrich)
shapiro.test(specscno)

#Alpha
alpha1=fisher.alpha(date1[,8:158])
alpha2=fisher.alpha(date2[,8:158])
alpha3=fisher.alpha(date3[,8:158])
alpha4=fisher.alpha(date4[,8:158])
plot(alpha1)
plot(alpha2)
plot(alpha3)
plot(alpha4)

#Gamma
gammadiv=with(date1, tapply(specnumber(date1[,8:158]),Habitat, mean))
plot(gammadiv)
gamma2=with(date2, tapply(specnumber(date2[,8:158]),Habitat, mean))
gamma3=with(date3, tapply(specnumber(date3[,8:158]),Habitat, mean))
gamma4=with(date4, tapply(specnumber(date4[,8:158]),Habitat, mean))
plot(gammadiv,gamma2,gamma3,gamma4)

#Beta
alpha1 <- with(date1, tapply(specnumber(date1[,8:158]), Habitat, mean))
alpha2 <- with(date2, tapply(specnumber(date2[,8:158]), Habitat, mean))
alpha3 <- with(date3, tapply(specnumber(date3[,8:158]), Habitat, mean))
alpha4 <- with(date4, tapply(specnumber(date4[,8:158]), Habitat, mean))



beta1=gammadiv/alpha1-1
beta2=gamma2/alpha2-1
beta3=gamma3/alpha3-1
beta4=gamma4/alpha4-1


````


```{r RDA DATE1}
#RDA analysis
dim(commdata)
colnames(commdata)!="Drosophilidae..Drosophila"
rdadate1=commdata[commdata$Date=="10.6.15",)]
#REMOVE FRUIT FLIES
rdadate1=commdata[commdata$Date=="10.6.15",which(colnames(commdata)!="Drosophilidae..Drosophila"&colnames(commdata)!="Drosophilidae..Microdrosophila"&colnames(commdata)!="Drosophilidae..Mycodrosophila")]
dim(rdadate1)

tree.hel.soil=merge(rdadate1,soildata, by="Plot")
dim(tree.hel.soil)
rownames(tree.hel.soil)=tree.hel.soil[,1]
tree.hel.soil=na.exclude(tree.hel.soil)
# Here is the global analysis. Can proceed  Use adj. R square as additional stopping criterion.
colnames(tree.hel.soil)
tree.hel.soil=tree.hel.soil[tree.hel.soil$EP=="Core"|tree.hel.soil$EP=="Transition",]
dim(tree.hel.soil)

hel.rda.fulsoil = rda(tree.hel.soil[,8:155], tree.hel.soil[,165:189])
anova(hel.rda.fulsoil)
RsquareAdj(hel.rda.fulsoil)
global.thresh=RsquareAdj(hel.rda.fulsoil)$adj.r.squared

dim(tree.hel.soil)
colnames(tree.hel.soil)
##Forward Selection to pick important tree species
#hel.rda.for=forward.sel(tree.hel.soil[,9:158], tree.hel.soil[,168:192], adjR2thresh=global.thresh)
#hel.rda.for
#names(tree.hel.soil)
#hel.rda.selsoil = rda(tree.hel.soil[,10:42],tree.hel.soil$ps1_short)
#anova(hel.rda.selsoil)
#RsquareAdj(hel.rda.selsoil)
#plot(hel.rda.selsoil)

###INVERT BY TREE DATA
colnames(tree.ringsum1)
dim(rdadate1)
inverttrees=merge(rdadate1,tree.ringsum)
dim(inverttrees)
invert.colsums=apply(inverttrees[,8:155],2,sum)

colnames(inverttrees)
invert.hel=inverttrees[,which(invert.colsums!=0)]
dim(invert.hel)

invert.hel=decostand(invert.hel, method="hellinger")
rownames(invert.hel)=invert.hel[,1]

tree.rowsums=apply(tree.ringsum3,1,sum)
tree.hel=tree.ringsum
tree.hel[,10:42]=tree.hel[,10:42]/tree.rowsums
tree.hel[,10:42]=sqrt(tree.hel[,10:42])
rownames(tree.hel)

invert.hel=invert.hel[invert.hel$TerrType!="S",]
tree.hel=tree.hel[tree.hel$Plot!="M4",]
tree.hel=tree.hel[tree.hel$Plot!="I3/4",]

tree.hel.soil=cbind(tree.hel,invert.hel[,6:67])
dim(tree.hel.soil)
rownames(tree.hel.soil)=tree.hel.soil[,1]
tree.hel.soil=na.exclude(tree.hel.soil)
# Here is the global analysis. Can proceed  Use adj. R square as additional stopping criterion.
colnames(tree.hel.soil)
#tree.hel.soil=tree.hel.soil[tree.hel.soil$EP=="Core",]
dim(tree.hel.soil)

hel.rda.fulsoil = rda(tree.hel.soil[,46:107],tree.hel.soil[,c(8,9,13,14,18,09,22,27,28,30,31,33,34,37)])
anova(hel.rda.fulsoil)
RsquareAdj(hel.rda.fulsoil)
global.thresh=RsquareAdj(hel.rda.fulsoil)$adj.r.squared
# Here is the forward selection command and then constructing a model with selected variables.
#hel.rda.for=forward.sel(tree.hel.soil[,8:158],tree.hel.soil[,c(159,160,164,165,169,170,173,178,179,81,182,184,185,188)], adjR2thresh=global.thresh)
#hel.rda.for
#names(tree.hel.soil)
#hel.rda.selsoil = rda(tree.hel.soil[,10:42] ~ as.matrix(tree.hel.soil[,c(52,54,56,57,58)]))
#anova(hel.rda.selsoil)
#RsquareAdj(hel.rda.selsoil)
#plot(hel.rda.selsoil)


###INVERTS BY PCMN
#to determine spatial autocorrelation
# First we perform PCNM to get the vectors
colnames(tree.hel.soil)
all.geog.dist=vegdist(tree.hel.soil[,8:9],method="euclid")
all.pcnm1=pcnm(all.geog.dist)
all.pcnmvecs=all.pcnm1$vectors
# If you can get the PCNM library to run, you could do the line below to select only significantly structured PCNMs
#tree.hel.all.pcnm=cbind(tree.hel.soil,all.pcnmvecs[,which(all.pcnm1$Moran_I[,2]<0.05)])
tree.hel.all.pcnm=cbind(tree.hel.soil,all.pcnmvecs)
names(tree.hel.all.pcnm)
# Now run step 1, global analysis
hel.rda.all.fulpcnm=rda(tree.hel.all.pcnm[,46:107], tree.hel.all.pcnm[,111:154])
anova(hel.rda.all.fulpcnm)
RsquareAdj(hel.rda.all.fulpcnm)
global.thresh=RsquareAdj(hel.rda.all.fulpcnm)$adj.r.squared
# now run step 2, the selection part
#hel.rda.all.forpcnm=forward.sel(tree.hel.all.pcnm[,10:42], tree.hel.all.pcnm[,77:120], #adjR2thresh=global.thresh)
#hel.rda.all.forpcnm
# Let's store a model using the selected variables only
#names(tree.hel.all.pcnm)
#hel.rda.all.selpcnm = rda(tree.hel.all.pcnm[,10:42] ~ as.matrix(tree.hel.all.pcnm[,c(77:81,83:86)]))
#anova(hel.rda.all.selpcnm)
#RsquareAdj(hel.rda.all.selpcnm)


##INVERTS BY ECOSYSTEM
#RDA analysis
invert.hel=inverttrees[,which(invert.colsums!=0)]
dim(invert.hel)
invert.hel=decostand(invert.hel, method="hellinger")
rownames(invert.hel)=invert.hel[,1]

#Just the CORE Plots
invert.hel=invert.hel[invert.hel$EP=="Core",]
hel.rda.fulsoil = rda(invert.hel[,8:67]~invert.hel$Habitat)
anova(hel.rda.fulsoil)
RsquareAdj(hel.rda.fulsoil)
global.thresh=RsquareAdj(hel.rda.fulsoil)$adj.r.squared

#Everything BUT the Transition
invert.hel=invert.hel[invert.hel$EP!="Edge",]
dim(invert.hel)
hel.rda.fulsoil = rda(invert.hel[,8:67]~invert.hel$Habitat)
anova(hel.rda.fulsoil)
RsquareAdj(hel.rda.fulsoil)
global.thresh=RsquareAdj(hel.rda.fulsoil)$adj.r.squared

````

```{r RDA DATE2}
#RDA analysis
dim(commdata)
colnames(commdata)
rdadate1=commdata[commdata$Date=="5.5.16",]

tree.hel.soil=merge(rdadate1,soildata, by="Plot")
dim(tree.hel.soil)
rownames(tree.hel.soil)=tree.hel.soil[,1]
tree.hel.soil=na.exclude(tree.hel.soil)
# Here is the global analysis. Can proceed  Use adj. R square as additional stopping criterion.
colnames(tree.hel.soil)
#tree.hel.soil=tree.hel.soil[tree.hel.soil$EP=="Core",]
#dim(tree.hel.soil)

hel.rda.fulsoil = rda(tree.hel.soil[,8:158],tree.hel.soil[,168:192])
anova(hel.rda.fulsoil)
RsquareAdj(hel.rda.fulsoil)
global.thresh=RsquareAdj(hel.rda.fulsoil)$adj.r.squared
# Here is the forward selection command and then constructing a model with selected variables.
#hel.rda.for=forward.sel(tree.hel.soil[,10:42], tree.hel.soil[,52:76], adjR2thresh=global.thresh)
#hel.rda.for
#names(tree.hel.soil)
#hel.rda.selsoil = rda(tree.hel.soil[,10:42] ~ as.matrix(tree.hel.soil[,c(52,54,56,57,58)]))
#anova(hel.rda.selsoil)
#RsquareAdj(hel.rda.selsoil)
#plot(hel.rda.selsoil)


###INVERT BY TREE DATA
colnames(tree.ringsum)
dim(tree.ringsum)
rownames(rdadate1)=rdadate1[,1]
inverttrees=merge(rdadate1,tree.ringsum3)
dim(inverttrees)
invert.colsums=apply(inverttrees[,8:158],2,sum)

colnames(invert.hel)
invert.hel=cbind(inverttrees$Plot,inverttrees[,which(invert.colsums!=0)])
invert.hel=decostand(invert.hel, method="hellinger")

dim(invert.hel)
colnames(invert.hel)

tree.rowsums=apply(tree.ringsum3,1,sum)
tree.hel=tree.ringsum
tree.hel[,10:42]=tree.hel[,10:42]/tree.rowsums
tree.hel[,10:42]=sqrt(tree.hel[,10:42])

dim(invert.hel)
dim(tree.hel)
invert.hel=invert.hel[invert.hel$TerrType!="S",]
rownames(invert.hel)=invert.hel[,1]
dim(invert.hel)
tree.hel=tree.hel[tree.hel$Plot!="M4",]

tree.hel.soil=cbind(tree.hel,invert.hel[,6:72])
dim(tree.hel.soil)
rownames(tree.hel.soil)=tree.hel.soil[,1]
tree.hel.soil=na.exclude(tree.hel.soil)
# Here is the global analysis. Can proceed  Use adj. R square as additional stopping criterion.
colnames(tree.hel.soil)
#tree.hel.soil=tree.hel.soil[tree.hel.soil$EP=="Core",]
dim(tree.hel.soil)

hel.rda.fulsoil = rda(tree.hel.soil[,46:112],tree.hel.soil[,c(8,9,13,14,18,09,22,27,28,30,31,33,34,37)])
anova(hel.rda.fulsoil)
RsquareAdj(hel.rda.fulsoil)
global.thresh=RsquareAdj(hel.rda.fulsoil)$adj.r.squared

###INVERTS BY PCMN
#to determine spatial autocorrelation
# First we perform PCNM to get the vectors
colnames(tree.hel.soil)
all.geog.dist=vegdist(tree.hel.soil[,8:9],method="euclid")
all.pcnm1=pcnm(all.geog.dist)
all.pcnmvecs=all.pcnm1$vectors
# If you can get the PCNM library to run, you could do the line below to select only significantly structured PCNMs
#tree.hel.all.pcnm=cbind(tree.hel.soil,all.pcnmvecs[,which(all.pcnm1$Moran_I[,2]<0.05)])
tree.hel.all.pcnm=cbind(tree.hel.soil,all.pcnmvecs)
tree.hel.all.pcnm=tree.hel.all.pcnm[tree.hel.all.pcnm$EP=="Core",]
# Now run step 1, global analysis
hel.rda.all.fulpcnm=rda(tree.hel.all.pcnm[,46:112], tree.hel.all.pcnm[,113:160])
anova(hel.rda.all.fulpcnm)
RsquareAdj(hel.rda.all.fulpcnm)
global.thresh=RsquareAdj(hel.rda.all.fulpcnm)$adj.r.squared
# NON significant - don't run step 2. To find step 2, see Blackwood et al code from Monographs paper

##INVERTS BY ECOSYSTEM
#RDA analysis
rdadate1=commdata[commdata$Date=="5.5.16",which(colnames(commdata)!="Drosophilidae..Drosophila"&colnames(commdata)!="Drosophilidae..Microdrosophila"&colnames(commdata)!="Drosophilidae..Mycodrosophila")]
inverttrees=merge(rdadate1,tree.ringsum3)
dim(inverttrees)
invert.colsums=apply(inverttrees[,8:158],2,sum)
invert.hel=cbind(inverttrees$Plot,inverttrees$EP,inverttrees$Habitat,inverttrees[,which(invert.colsums!=0)])
dim(invert.hel)
invert.hel=decostand(invert.hel, method="hellinger")
rownames(invert.hel)=invert.hel[,1]

#Just the CORE Plots
invert.helcore=invert.hel[invert.hel[,2]=="Core",]
hel.rda.fulsoil = rda(invert.helcore[,8:92]~invert.helcore[,3])
anova(hel.rda.fulsoil)
RsquareAdj(hel.rda.fulsoil)
global.thresh=RsquareAdj(hel.rda.fulsoil)$adj.r.squared

#Everything BUT the Transition
invert.heledge=invert.hel[invert.hel[,2]!="Edge",]
dim(invert.heledge)
hel.rda.fulsoil = rda(invert.heledge[,7:8:92]~invert.heledge[,3])
anova(hel.rda.fulsoil)
RsquareAdj(hel.rda.fulsoil)
global.thresh=RsquareAdj(hel.rda.fulsoil)$adj.r.squared


````

```{r RDA DATE3}
#RDA analysis
dim(commdata)
colnames(commdata)
rdadate1=commdata[commdata$Date=="8.10.16",]

tree.hel.soil=merge(rdadate1,soildata, by="Plot")
dim(tree.hel.soil)
rownames(tree.hel.soil)=tree.hel.soil[,1]
tree.hel.soil=na.exclude(tree.hel.soil)
# Here is the global analysis. Can proceed  Use adj. R square as additional stopping criterion.
colnames(tree.hel.soil)
tree.hel.soil=tree.hel.soil[tree.hel.soil$EP=="Core",]
#dim(tree.hel.soil)

hel.rda.fulsoil = rda(tree.hel.soil[,8:158], tree.hel.soil[,168:192])
anova(hel.rda.fulsoil)
RsquareAdj(hel.rda.fulsoil)
global.thresh=RsquareAdj(hel.rda.fulsoil)$adj.r.squared
# Here is the forward selection command and then constructing a model with selected variables.
#hel.rda.for=forward.sel(tree.hel.soil[,10:42], tree.hel.soil[,52:76], adjR2thresh=global.thresh)
#hel.rda.for
#names(tree.hel.soil)
#hel.rda.selsoil = rda(tree.hel.soil[,10:42] ~ as.matrix(tree.hel.soil[,c(52,54,56,57,58)]))
#anova(hel.rda.selsoil)
#RsquareAdj(hel.rda.selsoil)
#plot(hel.rda.selsoil)


###INVERT BY TREE DATA
colnames(tree.ringsum1)
dim(rdadate1)
inverttrees=merge(rdadate1,tree.ringsum)
dim(inverttrees)
rownames(inverttrees)=inverttrees[,1]
invert.colsums=apply(inverttrees[,8:158],2,sum)

invert.hel=cbind(inverttrees$Plot,inverttrees[,which(invert.colsums!=0)])
invert.hel=decostand(invert.hel, method="hellinger")
dim(invert.hel)
colnames(invert.hel)

tree.rowsums=apply(tree.ringsum3,1,sum)
tree.hel=tree.ringsum
tree.hel[,10:42]=tree.hel[,10:42]/tree.rowsums
tree.hel[,10:42]=sqrt(tree.hel[,10:42])

invert.hel=invert.hel[invert.hel$TerrType!="S",]
tree.hel=tree.hel[tree.hel$Plot!="I3/4",]
tree.hel=tree.hel[tree.hel$Plot!="N7",]


tree.hel.soil=cbind(tree.hel,invert.hel[,6:77])
dim(tree.hel.soil)
rownames(tree.hel.soil)=tree.hel.soil[,1]
tree.hel.soil=na.exclude(tree.hel.soil)
# Here is the global analysis. Can proceed  Use adj. R square as additional stopping criterion.
colnames(tree.hel.soil)
tree.hel.soil=tree.hel.soil[tree.hel.soil$EP=="Core",]
dim(tree.hel.soil)

hel.rda.fulsoil = rda(tree.hel.soil[,46:112],tree.hel.soil[,c(8,9,13,14,18,09,22,27,28,30,31,33,34,37)])
anova(hel.rda.fulsoil)
RsquareAdj(hel.rda.fulsoil)
global.thresh=RsquareAdj(hel.rda.fulsoil)$adj.r.squared

###INVERTS BY PCMN
#to determine spatial autocorrelation
# First we perform PCNM to get the vectors
colnames(tree.hel.soil)
all.geog.dist=vegdist(tree.hel.soil[,8:9],method="euclid")
all.pcnm1=pcnm(all.geog.dist)
all.pcnmvecs=all.pcnm1$vectors
# If you can get the PCNM library to run, you could do the line below to select only significantly structured PCNMs
#tree.hel.all.pcnm=cbind(tree.hel.soil,all.pcnmvecs[,which(all.pcnm1$Moran_I[,2]<0.05)])
tree.hel.all.pcnm=cbind(tree.hel.soil,all.pcnmvecs)
#tree.hel.all.pcnm=tree.hel.all.pcnm[tree.hel.all.pcnm$EP=="Core",]
# Now run step 1, global analysis
hel.rda.all.fulpcnm=rda(tree.hel.all.pcnm[,46:112], tree.hel.all.pcnm[,113:139])
anova(hel.rda.all.fulpcnm)
RsquareAdj(hel.rda.all.fulpcnm)
global.thresh=RsquareAdj(hel.rda.all.fulpcnm)$adj.r.squared
# NON significant - don't run step 2. To find step 2, see Blackwood et al code from Monographs paper


##INVERTS BY ECOSYSTEM
#RDA analysis
rdadate1=commdata[commdata$Date=="8.10.16",which(colnames(commdata)!="Drosophilidae..Drosophila"&colnames(commdata)!="Drosophilidae..Microdrosophila"&colnames(commdata)!="Drosophilidae..Mycodrosophila")]
inverttrees=merge(rdadate1,tree.ringsum3)
dim(inverttrees)
invert.colsums=apply(inverttrees[,8:158],2,sum)
invert.hel=cbind(inverttrees$Plot,inverttrees$EP,inverttrees$Habitat,inverttrees[,which(invert.colsums!=0)])
dim(invert.hel)
invert.hel=decostand(invert.hel, method="hellinger")
rownames(invert.hel)=invert.hel[,1]

#Just the CORE Plots
invert.helcore=invert.hel[invert.hel[,2]=="Core",]
hel.rda.fulsoil = rda(invert.helcore[,5:80]~invert.helcore[,3])
anova(hel.rda.fulsoil)
RsquareAdj(hel.rda.fulsoil)
global.thresh=RsquareAdj(hel.rda.fulsoil)$adj.r.squared

#Everything BUT the Transition
invert.heledge=invert.hel[invert.hel[,2]!="Edge",]
dim(invert.heledge)
hel.rda.fulsoil = rda(invert.heledge[,5:80]~invert.heledge[,3])
anova(hel.rda.fulsoil)
RsquareAdj(hel.rda.fulsoil)
global.thresh=RsquareAdj(hel.rda.fulsoil)$adj.r.squared



````
MARGINAL SIGNIFICANCE: Date 3, core plots only. Inverts~Tree. (0.097)

```{r RDA DATE4}
#RDA analysis
dim(commdata)
colnames(commdata)
rdadate1=commdata[commdata$Date=="10.15.16",]

tree.hel.soil=merge(rdadate1,soildata, by="Plot")
dim(tree.hel.soil)
rownames(tree.hel.soil)=tree.hel.soil[,1]
tree.hel.soil=na.exclude(tree.hel.soil)
# Here is the global analysis. Can proceed  Use adj. R square as additional stopping criterion.
colnames(tree.hel.soil)
tree.hel.soil=tree.hel.soil[tree.hel.soil$EP=="Core",]
#dim(tree.hel.soil)

hel.rda.fulsoil = rda(tree.hel.soil[,8:158], tree.hel.soil[,168:192])
anova(hel.rda.fulsoil)
RsquareAdj(hel.rda.fulsoil)
global.thresh=RsquareAdj(hel.rda.fulsoil)$adj.r.squared
# Here is the forward selection command and then constructing a model with selected variables.
#hel.rda.for=forward.sel(tree.hel.soil[,10:42], tree.hel.soil[,52:76], adjR2thresh=global.thresh)
#hel.rda.for
#names(tree.hel.soil)
#hel.rda.selsoil = rda(tree.hel.soil[,10:42] ~ as.matrix(tree.hel.soil[,c(52,54,56,57,58)]))
#anova(hel.rda.selsoil)
#RsquareAdj(hel.rda.selsoil)
#plot(hel.rda.selsoil)


###INVERT BY TREE DATA
colnames(tree.ringsum1)
dim(rdadate1)
inverttrees=merge(rdadate1,tree.ringsum)
dim(inverttrees)
rownames(inverttrees)=inverttrees[,1]
invert.colsums=apply(inverttrees[,8:158],2,sum)

invert.hel=cbind(inverttrees$Plot,inverttrees[,which(invert.colsums!=0)])
invert.hel=decostand(invert.hel, method="hellinger")
rownames(invert.hel)=invert.hel[,1]
dim(invert.hel)
colnames(invert.hel)

tree.rowsums=apply(tree.ringsum3,1,sum)
tree.hel=tree.ringsum
tree.hel[,10:42]=tree.hel[,10:42]/tree.rowsums
tree.hel[,10:42]=sqrt(tree.hel[,10:42])

invert.hel=invert.hel[invert.hel$TerrType!="S",]
tree.hel=tree.hel[tree.hel$Plot!="19",]
tree.hel=tree.hel[tree.hel$Plot!="B1/2",]
tree.hel=tree.hel[tree.hel$Plot!="I3/4",]
tree.hel=tree.hel[tree.hel$Plot!="M1",]
tree.hel=tree.hel[tree.hel$Plot!="N7",]
tree.hel=tree.hel[tree.hel$Plot!="P1/2",]
tree.hel=tree.hel[tree.hel$Plot!="P3/4",]
tree.hel=tree.hel[tree.hel$Plot!="S2",]
tree.hel=tree.hel[tree.hel$Plot!="Q1/2",]
tree.hel=tree.hel[tree.hel$Plot!="Q3/4",]
tree.hel=tree.hel[tree.hel$Plot!="Q5/6",]


tree.hel.soil=cbind(tree.hel,invert.hel[,6:69])
dim(tree.hel.soil)
rownames(tree.hel.soil)=tree.hel.soil[,1]
tree.hel.soil=na.exclude(tree.hel.soil)
# Here is the global analysis. Can proceed  Use adj. R square as additional stopping criterion.
colnames(tree.hel.soil)
#tree.hel.soil=tree.hel.soil[tree.hel.soil$EP=="Core",]
dim(tree.hel.soil)

hel.rda.fulsoil = rda(tree.hel.soil[,46:109],tree.hel.soil[,c(8,9,13,14,18,09,22,27,28,30,31,33,34,37)])
anova(hel.rda.fulsoil)
RsquareAdj(hel.rda.fulsoil)
global.thresh=RsquareAdj(hel.rda.fulsoil)$adj.r.squared

###INVERTS BY PCMN
#to determine spatial autocorrelation
# First we perform PCNM to get the vectors
colnames(tree.hel.soil)
all.geog.dist=vegdist(tree.hel.soil[,8:9],method="euclid")
all.pcnm1=pcnm(all.geog.dist)
all.pcnmvecs=all.pcnm1$vectors
# If you can get the PCNM library to run, you could do the line below to select only significantly structured PCNMs
#tree.hel.all.pcnm=cbind(tree.hel.soil,all.pcnmvecs[,which(all.pcnm1$Moran_I[,2]<0.05)])
tree.hel.all.pcnm=cbind(tree.hel.soil,all.pcnmvecs)
#tree.hel.all.pcnm=tree.hel.all.pcnm[tree.hel.all.pcnm$EP=="Core",]
# Now run step 1, global analysis
colnames(tree.hel.all.pcnm)
hel.rda.all.fulpcnm=rda(tree.hel.all.pcnm[,46:109], tree.hel.all.pcnm[,110:151])
anova(hel.rda.all.fulpcnm)
RsquareAdj(hel.rda.all.fulpcnm)
global.thresh=RsquareAdj(hel.rda.all.fulpcnm)$adj.r.squared
# NON significant - don't run step 2. To find step 2, see Blackwood et al code from Monographs paper

##INVERTS BY ECOSYSTEM
#RDA analysis
rdadate1=commdata[commdata$Date=="10.15.16",]
rdadate1=commdata[commdata$Date=="10.15.16",which(colnames(commdata)!="Drosophilidae..Drosophila"&colnames(commdata)!="Drosophilidae..Microdrosophila"&colnames(commdata)!="Drosophilidae..Mycodrosophila")]
inverttrees=merge(rdadate1,tree.ringsum3)
dim(inverttrees)
invert.colsums=apply(inverttrees[,8:158],2,sum)
invert.hel=cbind(inverttrees$Plot,inverttrees$EP,inverttrees$Habitat,inverttrees[,which(invert.colsums!=0)])
dim(invert.hel)
invert.hel=decostand(invert.hel, method="hellinger")
rownames(invert.hel)=invert.hel[,1]

#Just the CORE Plots
invert.helcore=invert.hel[invert.hel[,2]=="Core",]
hel.rda.fulsoil = rda(invert.helcore[,7:72]~invert.helcore[,3])
anova(hel.rda.fulsoil)
RsquareAdj(hel.rda.fulsoil)
global.thresh=RsquareAdj(hel.rda.fulsoil)$adj.r.squared

#Everything BUT the Transition
invert.heledge=invert.hel[invert.hel[,2]!="Edge",]
dim(invert.heledge)
hel.rda.fulsoil = rda(invert.heledge[7:72]~invert.heledge[,3])
anova(hel.rda.fulsoil)
RsquareAdj(hel.rda.fulsoil)
global.thresh=RsquareAdj(hel.rda.fulsoil)$adj.r.squared


````


ALL PLOTS on commdata$Habitat
Date 1 (10.6.15):   p=0.81
Date 2 (5.5.16):    p=0.645
Date 3 (8.10.16):   p=0.321
Date 4 (10.16.15):  p=0.036*

ONLy CORE PLOTS plots by habitat
Date 1 (10.6.15):   p=0.008*
Date 2 (5.5.16):    p=0.191
Date 3 (8.10.16):   p=0.435
Date 4 (10.16.15):  p=0.244

ALL PLOTS to soil variables:
Date 1 (10.6.15):   p=0.305
Date 2 (5.5.16):    p=0.943
Date 3 (8.10.16):   p=0.402
Date 4 (10.16.15):  p=0.115

CORE PLOTS ONLY to soil variables:
Date 1 (10.6.15):   p=0.294
Date 2 (5.5.16):    p=0.406
Date 3 (8.10.16):   p=0.58
Date 4 (10.16.15):  p=0.413

ALL PLOTS Over 1% of trees
Date 1 (10.6.15):   p=0.001*  ADJ R2: 0.974
Date 2 (5.5.16):    p=0.012*  ADJ R2: 0.112
Date 3 (8.10.16):   p=0.01*   ADJ R2: 0.056
Date 4 (10.16.15):  p=0.001*  ADJ R2: 0.332

CORE PLOTS ONLY
Date 1 (10.6.15):   p=0.001*  ADJ R2: 0.994
Date 2 (5.5.16):    p=0.001*  ADJ R2: 0.322
Date 3 (8.10.16):   p=0.328   ADJ R2: -0.001
Date 4 (10.16.15):  p=0.001*  ADJ R2: 0.481